Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-14 phd/dissertation/chapter5.tex
Renumber chapters

\chapter{Menger Game}

Results pertaining to the Menger game characterizing the Menger property.

\section{cut-and-paste}

  \begin{defn}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{prop}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{prop}

  \begin{defn}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{thm}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{thm}

  \begin{proof}
    Result due to Hurewicz.

    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.

    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.

    Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$. Then, since $F$ is choosing finite subsets, we may assume $F$ chooses some initial segement of the countable cover. In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$. And in that case, it's suffient to assume $F$ simply chooses a singleton subset of each cover. And finally, since choices made by $F$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $F$ previously.

    As a result, we have the following figure of a tree of plays which I need to draw:

    (Insert figure here.)

    Note that for $a,b\in\omega^{<\omega}$ and $m\leq n$, we know:
      \begin{enumerate}[(a)]
        \item $U_{a\concat m}\subseteq U_{a\concat n}$ \\ (for example, $U_{1627} \subseteq U_{1629}$ - increasing the final digit yields supersets)
        \item $U_a \subseteq U_{a\concat b}$ \\ (for example, $U_{1627}\subseteq U_{162789}$ - appending any sequence to the end yields supersets)
        \item $U_{a\concat m} \subseteq U_{a\concat n} \subseteq U_{a\concat n\concat b} \subseteq U_{a\concat n\concat b\concat m}$ \\ (for example: $U_{1627} \subseteq U_{1629283287}$ - injecting a subseqence with initial number larger than the original's final number, prior to the final number, yields supersets) 
      \end{enumerate}

    We may observe that if $F$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.

    Let $\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k}$. We claim that (1) $V_k^n$ is open, (2) $\mathcal{V}^n=\{V_0^n,V_1^n,\dots\}$ is increasing, and (3) $\mathcal{V}^n$ is a cover. Proofs:

    \begin{enumerate}
      \item
      Since due to (c) for each $b\in \omega^{\leq n} \setminus k^{\leq n}$, there is an $a\in k^{\leq n}$ with $U_{a\concat k} \subseteq U_{b\concat k}$: \[\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k} \cap \bigcap_{b\in \omega^{\leq n} \setminus k^{\leq n}} U_{b\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k}\] making $V_k^n$ a finite intersection of open sets.

      \item
      We show $V_k^0\subseteq V_{k+1}^0$:
      \[
        V_k^0 = U_k \subseteq U_{k+1} = V_{k+1}^0
      \]
      and then assume $V_k^{n}\subseteq V_{k+1}^{n}$:
      \[
        V_k^{n+1} = 
        \bigcap_{a\in{\omega}^{\leq n+1}} U_{a\concat k} = 
        V_k^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat k} \subseteq
        V_{k+1}^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat (k+1)} =
        V_{k+1}^{n+1}
      \]

      \item
      We easily see that $\mathcal{V}^0=\{U_0,U_1,\dots\}$ is a cover, and then assume $\mathcal{V}^n$ is a cover.

      Let $x\in X$ and pick $l<\omega$ such that $x \in V^n_l$. For $a \in l^{n+1}$ choose $l_a$ such that $x\in U_{a\concat l_a}$, giving
      \[ x \in \bigcap_{a\in l^{n+1}} U_{a\concat l_a} \]

      We will assume $k>l,l_a$ for all $a\in l^{\leq n+1}$.

      For any $a\in k^{n+1}\setminus l^{n+1}$ note that $a = b\concat c$ where $b\in l^{\leq n}$ and $c$ begins with a number $l$ or greater:
      \[
        V^n_l \subseteq 
        U_{b\concat l} \subseteq 
        U_{b\concat c} \subseteq
        U_{b\concat c\concat l_a} = 
        U_{a\concat l_a}
      \]

      Thus:
      \[ 
        x \in 
        V^n_l \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right) 
      \]
      \[
        =
        V^n_l \cap \left(\bigcap_{a\in k^{n+1}\setminus l^{n+1}} U_{a\concat l_a}\right) \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right)
      \]
      \[
        =
        V^n_l \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat l_a}\right)
      \]
      \[
        \subseteq
        V^n_k \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat k}\right)
      \]
      \[
        =
        V^{n+1}_k
      \]
    \end{enumerate}

    Finally, apply Menger to $\mathcal{V}^n$, resulting in the cover $\{V_{f(0)}^0, V_{f(1)}^1, \dots\}$, noting \[X = \bigcup_{n<\omega}V_{f(n)}^n \subseteq \bigcup_{n<\omega} U_{(f\rest n)\concat f(n)} = \bigcup_{n<\omega} U_{f\rest (n+1)}\]
  \end{proof}

  \begin{prop}
    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
  \end{prop}

  \begin{proof}
    Assume $X$ is compact. For each open cover played by $C$, pick a finite subcover, and this yields a winning tactical strategy.

    Assume $F$ has a winning $k$-tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
  \end{proof}

  \begin{prop}
    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
  \end{prop}

  \begin{proof}
    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $F$ picks the finite subcover of $C$'s open cover of $X_n$.
  \end{proof}

  For Menger's game, there is no useful distinction between a $k$-Markov strategy for $F$, and a $2$-Markov strategy.

  \begin{thm}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
  \end{thm}

  \begin{proof}
  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy. Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},m)$ for the following conditions on $\mc{W}_0,\dots,\mc{W}_{k-2},m$:
    \begin{itemize}
    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
    \item $m \leq (n+1)k$; in particular, for $i<k$, 
      \[
        \sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},(n+1)k+i)
        \subseteq 
        \tau(\mc{U},\mc{V},n+1) 
      \]
    \end{itemize}

  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
  \[
    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
    \dots
  \]

  So we have that
    \[
      \bigcup_{i<k, n<\omega} \sigma(
      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
      (n+1)k+i)
    \]
  is a cover for $X$, and as 
    \[
      \sigma(
      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
      (n+1)k+i)
      \subseteq 
      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
    \]
  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
  \end{proof}

  But there are spaces for which there is no Markov strategy, but there is a $2$-Markov strategy.

  In a question I posed to G, he answered:

  \begin{lem}
    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lem}

  \begin{proof}
    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$. Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of some countably infinite $P_n^*\subseteq P_n$ such that $P_n^* \subseteq \tau(\alpha, n)$.

    Choose $\beta \not\in \bigcup_{n<\omega} P_n$. Then for each $n<\omega$, pick $\alpha_n>\beta$ such that $\beta \not\in \tau(\alpha_n, n)$.
  \end{proof}

  Note that the one-point Lindel\"ofication of discrete $\omega_1$, $\oneptlind{\omega_1}$, is not $\sigma$-compact. With the above lemma, we may see that:

  \begin{ex}
    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
  \end{ex}

  \begin{proof}
    First, we see $F$ has a simple perfect information strategy: in response to the initial cover of $\oneptlind{\omega_1}$, $F$ chooses a co-countable neighborhood of $\infty$. On successive turns she may pick a single set from $C$'s covers to cover the countable remainder.

    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction. Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$.

    Using the sequence $\alpha_0, \alpha_1,\dots<\omega_1$ from the previous lemma, we consider the play $\mc{U}(\alpha_0),\mc{U}(\alpha_1),\dots$.

    As $\sigma$ was a winning strategy, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
  \end{proof}

  Telgarski showed in ``On Games of Topsoe'' that a metrizable space is $\sigma$-compact if and only if there exists a winning strategy for $F$ in the Menger game, and Scheepers gave a more direct proof later. We generalize Scheeper's proof to handle a number of cases.

  \begin{defn}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{defn}

  \begin{prop}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{prop}

  \begin{proof}
    The reverse implication is trivial.

    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and define $x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U$ for each $x\in X$. Then if we take a cover $\mc F = \{V_{x_i} : i<n\}$ of $Y$ by relative compactness, then $\{U_{x_i}:i<n\}$ is a finite cover of $\cl Y$, showing compactness.
  \end{proof}

  \begin{lem}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lem}

  \begin{proof}
    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$. Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$. Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$. Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$
  \end{proof}

  \begin{cor}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{cor}

  \begin{cor}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{cor}

  \begin{thm}
    For second-countable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F\markwin \mengame{X}$
      \end{enumerate}
  \end{thm}

  \begin{proof}.
    We need only show $(b)\Rightarrow(a)$, so let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable. Let $\mathfrak{C}$ be the collection of all countable covers of $X$. We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
      \begin{itemize}
        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{\<n\>}$ so that
          \[
            R_\emptyset = 
            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
          \]
        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{s\concat\<n\>}$ so that 
          \[
            R_s = 
            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
          \]
      \end{itemize}

    We quickly confirm that each $R_s$ is relatively compact as for each open cover $\mc{U}$ of $X$ we have the finite subcover $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of $R_s$.

    Finally, we claim that $X = \bigcup_{s\in\omega^{<\omega}} R_s$. If not, let $x$ be missed by every $R_s$, and define $f\in\omega^\omega$ such that $x\not\in \bigcup\sigma(\mc{U}_{f\rest1},\dots,\mc{U}_{f\rest n})$ for any $n$. Then $\mc{U}_{f\rest1},\mc{U}_{f\rest2},\dots$ is a counter to the winning strategy $\sigma$, a contradiction.
  \end{proof}

  \begin{cor}
    For metric spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{cor}

  \begin{ex}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{ex}

  \begin{proof}
  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular.

  Take open covers $\mc{U}_0,\mc{U}_1,\dots$. Define $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})$ to be a finite subcover of $[-n,n]\setminus C_n$ for some countable $C_n=\{c_{n,0}, c_{n,1}, \dots\}$. For $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})$, use any subcover of $\{c_{i,j} : i,j < n\}$. It is easily seen that $\sigma$ is a winning perfect information strategy.

  For any $A=\{x_n:n<\omega\} \in [R]^\omega$, we may choose the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$ of $R$ with no finite subcover. Thus all relatively compact sets are finite, and the countable union of finite sets cannot contain $R$, making $R$ not $\sigma$-(relatively compact).
  \end{proof}

  \begin{ex}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
  \end{ex}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space.

  To see that $R$ is $\sigma$-relatively compact, it suffices to show that $[a,b]\setminus\mathbb{Q}$ is relatively compact. Let $\mc U$ be a cover of $R$, and let $\mc U'$ fill in the missing rationals for any open set in $\mc U$. There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since $\mc U'$ contains open sets from the Euclidean topology. Let $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$ is relatively compact.
  \end{proof}

  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.

  \begin{defn}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{defn}

  \begin{defn}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{defn}

  \begin{lem}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lem}

  \begin{proof}
    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).

    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction. Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.

    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$. Let $g_0=f_{\alpha_0}$, and assuming $g_n\alcomp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\alcomp f_{\alpha_{n+1}}$ with coinfinite range. Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \alcomp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite. So let
    \[
      f_\gamma(\beta) = \left\{
      \begin{array}{ll}
        g(\alpha_{2n}) & \beta = \alpha_n \\
        g(\beta) & \text{otherwise}
      \end{array}
      \right.
    \]
    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\alcomp f_\alpha$.
  \end{proof}

  \begin{thm}
    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
  \end{thm}

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \alcomp f_\beta$. For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $\oneptlind{\omega_1}\setminus\gamma(\mc U)$ is in a refinement of $\mc V$. Then $r_{\mc V}$ defined by
      \[
        r_{\mc V}(x) = \left\{
      \begin{array}{ll}
        0 & x\in\oneptlind{\omega_1}\setminus\gamma(\mc V) \\
        f_{\gamma(\mc V)}(x)+1 & x\in\gamma(\mc V)
      \end{array}
      \right.
      \] 
    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
      \[
        p(\mc U,\mc V) = \{\alpha<\min(\gamma(\mc U),\gamma(\mc V)) : f_{\gamma(\mc U)}(\alpha)<f_{\gamma(\mc V)}(\alpha)\}
      \]
    is finite.
  \end{proof}

  \begin{thm}
    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
  \end{thm}

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
        \begin{itemize}
          \item For all $n\leq N$, 
            \[
              r_{\mc U_{n+1}}(x)\leq N+1
            \] 
            and thus $x\in c(\mc U_{N+1},N+1)$.
          \item For some $n \leq N$, 
            \[
              r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
            \]
           and thus $x\in p(\mc U_n,\mc U_{n+1})$
         \end{itemize}
      \end{itemize}
  \end{proof}

  \begin{cor}
    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
  \end{cor}

  \begin{defn} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{defn}

  \begin{prop}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{prop}

  \begin{proof}
    Let $A_\alpha=\{\alpha\cdot\omega+n:n<\omega\}\in[\kappa]^\omega$ and $f_{A_\alpha}:A_\alpha\to\omega$ be injective for $\alpha<\kappa$. Since there are $\kappa>|[\omega]^\omega|$ different $A_\alpha$, there must be $\alpha,\beta$ where $\text{ran}(f_{A_\alpha})=\text{ran}(f_{A_\beta})$. Then there is no way to define $f_{A_\alpha\cup A_\beta}$ so that it is almost compatible with both $f_{A_\alpha}$ and $f_{A_\beta}$.
  \end{proof}

  \begin{thm}
    $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
  \end{thm}

  \begin{proof}
    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$. For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$. Then $r_{\mc V}$ defined by 
      \[
        r_{\mc V}(x) = \left\{
      \begin{array}{ll}
        0 & x\in\oneptlind{\kappa}\setminus A(\mc V) \\
        f_{A(\mc V)}(x)+1 & x\in A(\mc V)
      \end{array}
      \right.
      \]

    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
      \[
        p(\mc U,\mc V) = \{\alpha\in A(\mc U)\cap A(\mc V) : f_{A(\mc U)}(\alpha)<f_{A(\mc V)}(\alpha)\}
      \]
    is finite.
  \end{proof}

  \begin{cor}
    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
  \end{cor}

  \begin{defn}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.

    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{defn}

  \begin{defn}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$ 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{defn}

  \begin{lem}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lem}

  \begin{proof}
    If $|\{\dom(p):p\in P\}|>\omega$, we will use the $\Delta$-system lemma to find an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)\cap\dom(q)=\mc R$. Otherwise, we may fix an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)=\dom(q)=\mc R$.

>>>>

\chapter{Locally Finite Games}

Results pertaining to the Locally Finite games related to $W$ games.

\section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is paracompact
      \item $\pl K \uparrow \lfklgame{X}$.
    \end{itemize}
\end{thm}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is metacompact
      \item $\pl K \tactwin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is $\sigma$-metacompact
      \item $\pl K \markwin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\begin{obs}
  The following are equivalent for any space $X$:
    \begin{itemize}
      \item $X$ is compact
      \item $\pl K \ktactwin{0} \lfkpgame{X}$.
    \end{itemize}
\end{obs}

\begin{thm}
  $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
  countably compact space.
\end{thm}

\begin{thm}
  $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
\end{thm}

\begin{thm}
  The following are equivalent for any locally compact space $X$:
    \begin{itemize}
      \item $X$ is Lindel\"of.
      \item $X$ is $\sigma$-compact.
      \item $X$ is hemicompact.
      \item $\pl K \prewin G_{K,L}(X)$.
      \item $\pl K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{thm}

\begin{thm}
  The following are equivalent for any Hausdorff $k$-space $X$:
    \begin{itemize}
      \item $X$ is hemicompact.
      \item $X$ is $k_{\omega}$.
      \item $\pl K \prewin \lfklgame{X}$.
      \item $\pl K \prewin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\section{Non-locally compact spaces}

\begin{prop}
  If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
  then $K\not\prewin \lfklgame{X}$.
\end{prop}

\begin{prop}
  If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
  then $K \not\prewin \lfkpgame{X}$
  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
\end{prop}

\begin{thm}
  Then there is an ultrafilter $\mathcal{F}$ such that
  then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
\end{thm}

\begin{thm}
  Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
  Then $P \win \lfkpgame{M}$.
\end{thm}

\begin{thm}
  Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
  Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
\end{thm}

(TODO: Maybe consider claim
$K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)

\section{Cantor tree space example}

\begin{ex}
  Let $X$ be a zero-dimensional, compact L-space
  (hereditarally Lindeloff and non-separable).
  It is a fact that there exists a point-countable collection
  $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
  also true that any point-finite subcollection of $\mathcal{U}$ is countable.

  Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
  Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
  $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

  Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
  tree of $2^{<\omega}$ copies of $X$, and where
  \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
  is an open set about each $c_\alpha$.
\end{ex}

\begin{prop}
$K \win \lfkpgame{\mathbb{X}}$.
\end{prop}

\begin{thm}(cor of G, game-theoretic proof by me)
$K\not\tactwin\lfkpgame{\mathbb{X}}$.
\end{thm}

\begin{thm}
$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
\end{thm}
